---
title: "International Monitoring Key Highlights - `r Sys.Date()`"
author: "Murad Khrais"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F)

# Load in packages to get started
source("scripts/international_monitoring.R")
```

## Key Highlights:

The current 28-day reporting interval is ending in `r current_interval`.

The previous 28-day reporting interval is ending in `r previous_interval`.

## Data:

### Case Increases (Region Level)

```{r, results='asis'}
# Convert the result vector to a bullet list format
bullet_list <- map_chr(case_inc_region(region_who_cases), function(item) {
  glue("- {item}")
})


# Print the bullet list
#cat(paste(bullet_list, collapse = "\n"))
writeLines(bullet_list, sep = "
           
")
```






#### The change in case counts in the last 28-day reporting interval relative to the previous 28-day interval for each of the WHO regions is shown below:

```{r message=FALSE, , echo=FALSE}
if (nrow(df_reg_case)<=1){
  cat(paste(bullet_list, collapse = "\n"))
} else {
  column_spec(kable(as.data.frame(df_reg_case %>% mutate(Region = WHO_region, Cases = Cases_quadriweekly, Cases_prev = Cases_PreviousWeek, Perc_chng = case_perc_change) %>% select(Cases, Cases_prev, Perc_chng)), col.names = c("Region", "Cases", "Prior Cases", "% Change"), format = "html", align = "lccr"), column = 1:4, width = "3cm")
}

```






### Death Increases (Region Level)

```{r, results='asis'}
# Convert the result vector to a bullet list format
bullet_list <- map_chr(death_inc_region(region_who_death), function(item) {
  glue("- {item}")
})

# Print the bullet list
#bullet_output <- cat(paste(bullet_list, collapse = "\n"))
writeLines(bullet_list, sep = "
           
")
```


#### The regions that have experienced an increase of \>1% in death counts in the last 28-day reporting interval relative to the previous 28-day interval (if any) are shown below:

```{r message=FALSE,  echo=FALSE, warning=FALSE}
if (nrow(df_reg_death)<=1){
  cat(paste(bullet_list, collapse = "\n"))
} else {
  column_spec(kable(as.data.frame(df_reg_death %>% mutate(Region = WHO_region, Deaths = Deaths_quadriweekly, Deaths_prev = Deaths_PreviousWeek, Perc_chng = death_perc_change) %>% select(Deaths, Deaths_prev, Perc_chng)), col.names = c("Region", "Deaths", "Prior Deaths", "% Change"), format = "html", align = "lccr"), column = 1:4, width = "3cm")
}
```






### Case Increases (Country Level)

`r country_case_list`

```{r message=FALSE, warning=FALSE, results='asis'}
# Convert the result vector to a bullet list format
bullet_list <- map_chr(case_inc_country(region_cases), function(item) {
  glue("- {item}")
})

# Print the bullet list
#cat(paste(bullet_list, collapse = "\n"))
writeLines(bullet_list, sep = "
           
")
```


#### The countries that have experienced an increase of \>20% in case counts in the last 28-day reporting interval relative to the previous 28-day interval are shown below:

```{r , echo=FALSE}
if (nrow(df_case)<=1){
  cat(paste(bullet_list, collapse = "\n"))
} else {
  column_spec(kable(as.data.frame(df_case %>% mutate(Region = WHO_region, Cases = Cases_quadriweekly, Cases_prev = Cases_PreviousWeek, Perc_chng = case_perc_change) %>% select(Country, Region, Cases, Cases_prev, Perc_chng)), col.names = c("Country", "Region", "Cases", "Prior Cases", "% Change"), format = "html", align = "lcccr"), column = 1:5, width = "4cm")
}
```






### Death Increases (Country Level)

`r country_death_list`

```{r message=FALSE, warning=FALSE, results='asis'}
# Convert the result vector to a bullet list format
bullet_list <- map_chr(death_inc_region(region_death), function(item) {
  glue("- {item}")
})

# Print the bullet list
#cat(paste(bullet_list, collapse = "\n"))
writeLines(bullet_list, sep = "
           
")
```


#### The countries that have experienced an increase of \>20% in case counts in the last 28-day reporting interval relative to the previous 28-day interval are shown below:

```{r, echo=FALSE}
if (nrow(df_death)<=1){
  cat(paste(bullet_list, collapse = "\n"))
} else {
  column_spec(kable(as.data.frame(df_death %>% mutate(Region = WHO_region, Deaths = Deaths_quadriweekly, Deaths_prev = Deaths_PreviousWeek, Perc_chng = death_perc_change) %>% select(Country, Region, Deaths, Deaths_prev, Perc_chng)), col.names = c("Country", "Region", "Cases", "Prior Cases", "% Change"), format = "html", align = "lcccr"), column = 1:5, width = "4cm")
}
```






## Variant Distributions:

### In countries with case increases:

Lineage distributions, over the past 8 months, in countries that have experienced an increase of \>20% in case counts in the last 28-day reporting interval relative to the previous 28-day interval are shown below.

```{r echo=FALSE, message=FALSE, warning=FALSE}
plotAllLineagesByLocation_case_inc(n_month = 3)
```

### In countries with death increases:

Lineage distributions, over the past 8 months, in countries that have experienced an increase of \>20% in death counts in the last 28-day reporting interval relative to the previous 28-day interval are shown below.

```{r echo=FALSE, message=FALSE, warning=FALSE}
plotAllLineagesByLocation_death_inc(n_month = 3)
```
